---
title: "cgmr: continous glucose monitoring for R"
date: "`r Sys.Date()`"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


Continuous Glucose Monitoring Package for R

Process raw CGM data from Freestyle Libreview, Levels, Nutrisense and others.

# Prerequisites

Download a CSV file from Libreview.com

```{r showTypical, message = FALSE}
library(tidyverse)
library(lubridate)
library(cgmr)

cgm_sample <- glucose_df_from_libreview_csv(system.file("extdata", package = "cgmr", "Firstname1Lastname1_glucose.csv"))

glucose_records <- cgm_sample 
notes_records <- notes_df_from_glucose_table(glucose_records)

head(glucose_records)

head(notes_records)



```


The most important function, `food_times_df_fast()` looks through all glucose and notes records to return a dataframe of times during a time interval after eating a specific food, in this case "Keto Bar", which the CGM wearer entered in the Notes field of the app.

```{r showFoodTimes, message = FALSE}


ft <- food_times_df_fast(glucose_records, notes_records, foodname = "keto bar")

ft
```


And of course you can easily plot the results

```{r plotFoodTimes}

ft %>% ggplot(aes(x=t, y = value, color = meal)) + geom_line()


```
